### 2021-09-28 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
conclusion and edits

The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.

>>>>

\hl{The values for the three non-charging cycle models with a focus on producing positive alternator power (provide electrical power to the grid), 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON,} are displayed in Table \ref{tab-noncharg}.
